### 2021-12-11 thesis/tex/DCtheory.tex
update

% \documentclass[draft=True]{thesis}
% \usepackage[margin=0.5in]{geometry}
% \usepackage{graphicx, slashed, siunitx}
% \usepackage[utf8]{inputenc}
% \usepackage{xr-hyper}
% \input{commands}
% \begin{document}
\section{DeepCore}\label{ch:DCmethod}
In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
They are applied as correction factors using the best-fit points from the DeepCore 2019 $\nu_\tau$ appearance 
analysis~\cite{DC2019tauappearance}.

@@

The oscillation parameters used on our DeepCore simulations are from the
best-fit in the global analysis in~\cite{nufit}: $\theta_{12} = \SI{33.44}{\degree},\, \theta_{13} = \SI{8.57}{\degree},\, \Delta m^2_{21} =  \SI{7.42}{\electronvolt^2}$, and we 
marginalize over $\dm$ and $\theta_{23}$.

\section{PINGU}
The methodology behind the PINGU simulations are the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

\begin{align}\label{eq:PINGUparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm[31] =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
% \bibliographystyle{nature}
% \bibliography{ref.bib}
% \end{document}

>>>>

\section{DeepCore}\label{ch:DCmethod}
In this part, we use the publicly available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disappearance analysis~\cite{DC2018mudisappearance}.

The detector systematics include ice absorption and scattering, and overall, lateral, and head-on optical efficiencies of the DOMs. 
They are applied as correction factors using the best-fit points from the 2019 DeepCore $\nu_\tau$ appearance 
analysis~\cite{DC2019tauappearance}.

@@

\section{PINGU}
The methodology behind the PINGU simulations is the same as with our DeepCore study~. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU Monte Carlo is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate `data' by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

\begin{align}\label{eq:PINGUparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm[31] =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0^\circ\,.
\end{align}

### 2021-12-11 thesis/tex/ICintro.tex
update

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
\end{figure}

@@

So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
information in Table~\ref{table:events}, containting classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
    zenith angle dependence, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
\end{figure}

@@

So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
information in Table~\ref{table:events}, containing classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.

### 2021-12-11 thesis/tex/ICtheory.tex
update

Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the leptons are exposed to.
While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself. Energy-wise, the situation here is completely reverse from the flux. 
Increasing linearily with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.

@@

So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publically released by the 
collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
The "pdg" column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
to an $\anm$. Here we note a crucial property of the IceCube dataset that will impact our analysis: the MC released by the collaboration
only includes simulated muon events.

@@

Note that since atmospheric neutrino flux scales as $E^{-2.7}$, the log-normal Gaussian $R(E^r, E^t)$ as $E^{-2}$,
and the effective area is approximately linear in $E$.
Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic dropoff, the event count as 
observed by IceCube will be lower and lower as we probe higher energies, severely limiting our confidence in \si{\TeV} analyses due to 
lower statistical significance.

@@

\begin{figure}[ht]
    \begin{center}
       \includegraphics[width=0.7\linewidth]{figures/IC_MC_gpr.pdf}
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}.
    Color indicates the frequency of each simulated point.
    Shaded area shows the 99th percentile limits predicted by the regressor trained on this set. It is within this band 
    that then will sample the $\Etrue$ values for each $\Ereco$.}\label{fig:IC_MC_gpr}
 \end{figure}

@@

In Fig.~\ref{fig:IC_MC_norm}, we present the IceCube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
with our null hypothesis times a constant factor. 
We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0$ for simplicity. The values used are
\begin{align}\label{eq:nufitparams}
    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.

>>>>

Here, $\Aeff$ has been averaged over $\Aeff_\mu$ and $\Aeff_{\bar{\mu}}$ by the collaboration. Thus, both $\mu$ and $\bar\mu$ will on average, experience the same $\Aeff$ in our model. 
Just as with the fluxes, we interpolate this in $\Etrue$ and $\ztrue$, and show the result in Fig.~\ref{fig:aeff}
Since the IceCube array is slightly rectangular, the zenith angle affects the cross-sectional area to which the array the leptons are exposed to.
While the flux was almost flat in $\ztrue$, the introduction of the zenith dependent $\Aeff$ will make the result slightly more zenith dependent than the flux itself. Energy-wise, the situation here is completely reverse from the flux. 
Increasing linearly with energy, the effective area of the detector approaches its geometrical area of \SI{1e6}{\metre^2} but is still only in the single-digit range at \si{\TeV} energies.

@@

So how do we then obtain $\sigma_{x^r}(x^t)$ and $\mu(x^t)$ needed to construct the Gaussian? A Monte Carlo sample publicly released by the 
collaboration has all the ingredients that we need~\cite{IC2016}. In Table.~\ref{table:IC_MC} we show a selection of the data.
The "pdg" column refers to the Monte Carlo particle classification, where 13 is the tag for $\nm$, while -13 refers
to an $\anm$. Here we note a crucial property of the IceCube dataset that will impact our analysis: the MC released by the collaboration
only includes simulated muon events.

@@

Note that since atmospheric neutrino flux scales as $E^{-2.7}$, the log-normal Gaussian $R(E^r, E^t)$ as $E^{-2}$,
and the effective area is approximately linear in $E$.
Thus, the event count in~\ref{eq:ICevents} will be proportional to $E^{-1.7}$. Having almost a quadratic drop-off, the event count as 
observed by IceCube will be lower and lower as we probe higher energies, severely limiting our confidence in \si{\TeV} analyses due to 
lower statistical significance.

@@

\begin{figure}[ht]
    \begin{center}
       \includegraphics[width=0.7\linewidth]{figures/IC_MC_gpr.pdf}
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}.
    The color indicates the frequency of each simulated point.
    Shaded area shows the 99th percentile limits predicted by the regressor trained on this set. It is within this band 
    that then will sample the $\Etrue$ values for each $\Ereco$.}\label{fig:IC_MC_gpr}
 \end{figure}

@@

In Fig.~\ref{fig:IC_MC_norm}, we present the IceCube Monte Carlo obtained from their 2020 sterile analysis~\cite{IC2020}, along
with our null hypothesis times a constant factor. 
We used the best-fit values from NuFit~\cite{nufit} with the exception of the CP-violating phase $\delta_\text{CP}$, which was set to $0^\circ$ for simplicity. The values used are
\begin{align}\label{eq:nufitparams}
    \theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0^\circ\,.
\end{align}

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in red in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.

### 2021-12-11 thesis/tex/nsiResults.tex
update

\section{Constraining the NSI parameters}\label{sec:constraining}
%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
incertainty.

@@

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The detectors experience an uncorrelated systematic error, which comes from the muon background, 
i.e. events misclassified as muons from 
$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
For IceCube events, we scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
to be neglible~\cite{PINGUletter}.
The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
We consider best, normal, and worst-case scenarios in IceCube using
$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$.
For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.
{\renewcommand{\arraystretch}{1.2}
\begin{table}
   \centering
   \begin{tabular}{lccc}
      \hline \hline
      Experiment & Best case & Baseline & Worst case \\
      \hline
      IceCube & $5\%$ & $10\%$ & $15\%$ \\
      PINGU & $0\%$ & $3\%$ & $5\%$ \\
      \hline \hline
   \end{tabular}
   \caption{Our definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
\end{table}

>>>>

\section{The NSI Hypothesis}\label{sec:constraining}
%TODO Ch 5.2 write what new things we have in the sterile analysis/chi2. Ie that NSI is showing in GeV -> deep core 
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

@@

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The detectors experience an uncorrelated systematic error, which comes from the muon background, 
i.e. events misclassified as muons from 
$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
For IceCube events, we scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
to be negligible~\cite{PINGUletter}.
The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.

We treat the uncorrelated systematic uncertainties differently for each detector. For IceCube, we set $\sigma_{ij}^\text{syst} = f\sqrt{N_{ij}^\text{data}}$.
We consider best, normal, and worst-case scenarios in IceCube using
$f=5\%$, $10\%$, and $15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $5\%$.
For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.
{\renewcommand{\arraystretch}{1.2}
\begin{table}
   \centering
   \begin{tabular}{lccc}
      \hline \hline
      Experiment & Best case & Baseline & Worst case \\
      \hline
      IceCube & $5\%$ & $10\%$ & $15\%$ \\
      PINGU & $0\%$ & $3\%$ & $5\%$ \\
      \hline \hline
   \end{tabular}
   \caption{Our definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
\end{table}

### 2021-12-11 thesis/tex/nsiTheory.tex
update

\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and flavor 
oscillations force us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas, but failing in others.

@@

Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
theory will have different interactions than those we presently know. These new interactions can be parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
Following the discussion in~\cite{tommyNSI}, we see that the NSI parameters $\epsilon$ resulting from six-dimensional operators have the scale
\begin{align}
    \epsilon \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory above electroweak scale, 
we then predict that the parameters contribute with at most a factor of $10^{-2}$ to the standard matter effect, decreasing quadratically.

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making them much more dependent on each other.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}%TODO subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilites simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

@@

Now we will compare the probability plots with the final event counts in DeepCore. It is not enough to only study the effect at probability level, since that is in true quantities. Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets smeared away in the reconstruction, and not showing up at all in the data. In general, features showing at probability level are often washed out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.

@@

% \end{document}

>>>>

\section{Non-Standard Interactions}\label{sec:nsiTheory}
We have no reason to believe that the Standard Model 
gauge group is the complete picture. We have already seen how the failure of the Standard Model to predict neutrino masses and 
oscillations forces us to amend it. 
Just as the electroweak theory $SU(2)_L \times U(1)_Y$ is 
spontaneously broken to $U(1)_{EM}$, a higher order theory at a different energy scale with completely different
properties might undergo a similar spontaneous symmetry break at high energies, 
producing at lower energies the Standard Model that we know. In fact, 
just as the fermion masses originate from the electroweak symmetry breaking, the neutrino masses might be generated from 
another broken symmetry resulting in the Standard Model gauge group.
In this sense, the Standard Model might be considered 
an effective low energy theory, which is yields impressive results in some areas, but failing in others.

@@

Following the approach of the Standard Model that the group generators uniquely determine the gauge bosons, a different gauge
theory will have different interactions than those we presently know. These new interactions can be parametrized as model-independent four-fermion effective operators \cite{salvadoNSI,nsiFarzan}.
Following the discussion in~\cite{tommyNSI}, we see that the NSI parameters $\epsilon$ resulting from six-dimensional operators have the scale
\begin{align}
    \epsilon \propto \frac{m_W^2}{m_{\epsilon}^2} \sim \frac{10^{-2}}{m_\epsilon^2}\,
\end{align} 
in \si{\TeV}, so the new interactions generated at a mass scale of $m_\epsilon = \SI{1}{TeV}$ will produce parameters in the order of $10^{-2}$, 
two magnitudes below the standard matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory above electroweak scale, 
we then predict that the parameters contribute with at most a factor of $10^{-2}$ to the standard matter effect, decreasing quadratically.

@@

Since all standard matter potentials are diagonal, 
the elements $\epsilon_{\a\b},\, \a = \b$ will directly adjust the matter potential felt 
by flavor $\a$. The off-diagonal terms have a more interesting theoretical implication as they open up matter interactions across flavors. Remember, in the Standard model,
we are restricted to weak interactions that conserve lepton flavor. However, an off-diagonal NSI parameter allows flavor transitions during matter interactions. Thus,
the off-diagonal elements constitute new sources of flavor violation.
Moreover, $\epsilon_{\a\b}$ modifies the $\nu_\a \to \nu_\b$ transition independently
of the mixing matrix. Thus, we are not confined to the parameters of the mixing matrix: now we have introduced the 
possibility of additional interactions that can cause the flavor change. Moreover, since we have 6 NSI parameters, and the PMNS
matrix is parametrized with only 3 parameters, we have more degrees of freedom when adjusting the probabilities using the NSI matrix. Each term in the PMNS matrix consists of at least
two of the three mixing angles, making the individual angles more inter-dependent than the NSI parameters, since combinations of them must satisfy the constraints of the matrix elements.

@@

Moving on to $\eem$ and Fig.~\ref{fig:eem_eet_probs}, we see that both probabilities has shifted downwards for $\Etrue > \SI{500}{\GeV}$.
In Fig.~\ref{fig:eem_eet_probs}, we see that the muon channel remains largely unaffected of the value of $\eet$ as we expected. The exception of this lies 
in the DeepCore region of rapid oscillations, where mixing is more violent. 
\begin{figure}
    \begin{center}
        %TODO: subplots and fix labels in parahgraph aboveto match them
        \includegraphics[width=0.99\textwidth]{figures/emt_probs.pdf}
        \includegraphics[width=0.99\textwidth]{figures/ett_probs.pdf}
        \caption{\emph{Top panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\emt = 0.02$. All other NSI parameters are fixed to zero. In the \si{\GeV} range, $\emt$ shifts the oscillations to the right for $\nm$, and to the left for $\anm$. At \si{\TeV} energies, both probabilities simply get shifted down, resulting in a net reduction of track events.
        \emph{Bottom panel:} Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\ett = 0.05$. All other NSI parameters are fixed to zero. $\ett$ does not affect the probabilities above \SI{100}{\GeV} and this parameter is thus unable to be constrained by tracks in IceCube in our study. However, the dampening of the $\anm$ survival probability will be visible to DeepCore and PINGU, since it occurs within their energy ranges.}
        \label{fig:emt_ett_probs}
    \end{center}
\end{figure}

@@

Now we will compare the probability plots with the final event counts in DeepCore. It is not enough to only study the effect at probability level, since that is in true quantities. Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets smeared away in the reconstruction, and not showing up at all in the data. In general, features showing at probability level are often averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.

@@
